---
title: "Monkeypox Data Explorer"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: https://github.com/hossainlab/monkeypox
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(highcharter)
library(gt)
library(htmltools)
library(viridis)
library(echarts4r)
## Data cleaning 
library(data.table)
library(dplyr)
library(tidyr)
library(magrittr)
library(purrr)
library(forcats)

## printing 
library(glue)


## Maps and Plots
library(plotly)
library(leaflet)
library(leafpop)
library(RColorBrewer)


# Dates
library(lubridate) 

## For displaying tables
library(DT)
theme_set(theme_classic())
```

```{r, data-import, include=FALSE}
data <- read.csv("https://raw.githubusercontent.com/owid/monkeypox/main/owid-monkeypox-data.csv", stringsAsFactors = TRUE)

data$date <- as.Date(data$date)
```

```{r, colors, include=FALSE}
confirmed_color <- "lightsteelblue"
active_color <- "orange"
new_deaths_color <- "limegreen"
death_color <- "red"
```


Sidebar {.sidebar}
=======================================================================

### Monkeypox Data Explorer
Visualizing the data produced by the World Health Organization on the 2022 monkeypox outbreak.

- Monkeypox is a viral disease that occurs mostly in central and western Africa. 
-  It can occur in humans and some other animals.
- Sources:  [World Health Research Organization](https://extranet.who.int/publicemergency/)


Built by [Md. Jubayer Hossain]()



Overview  
=======================================================================

Row
-----------------------------------------------------------------------

### Confirmed Cases {.value-box}

```{r}
confirmed <- format(max(data$total_cases), big.mark = ",")
valueBox(value = confirmed, 
         caption = "Total Confirmed Cases", 
         color = confirmed_color)
```


### New Cases {.value-box}
```{r}
active <- format(max(data$new_cases), big.mark = ",")
valueBox(value = active, 
         caption = "Total New Cases", 
         color = active_color)
```

### Confirmed Deaths {.value-box}
```{r}
deaths <- format(max(data$total_deaths), big.mark = ",")
valueBox(value = deaths, 
         caption = "Total Deaths", 
         color = death_color)
```

### New Deaths {.value-box}
```{r}
new_deaths <- format(max(data$new_deaths), big.mark = ",")
valueBox(value = new_deaths, 
         caption = "Total New Deaths", 
         color = "purple")
```


Row 
-----------------------------------------------------------------------

### Number of Confirmed Cases by Location {data-width=700}

```{r}
data %>%
  e_charts(location) %>%
  e_map(total_cases) %>%
  e_visual_map() %>%
  e_theme("infographic") %>%
  e_visual_map_range(selected= list(0,200))
```


### Number of Confirmed Cases by Location (Top 15 Countries) {data-width=340}

```{r}
# Most cases by countries 
data %>% 
  group_by(location) %>% 
  summarise(Confirmed = max(total_cases)) %>% 
  arrange(desc(Confirmed)) %>% 
  head(15) %>% 
  hchart('column', hcaes(x = location, y = Confirmed, color = viridis::mako(n = 15))) %>%   hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Number of Confirmed Cases: </b> {point.y} <br>') %>% 
  hc_credits(enabled = TRUE, text = '@Jubayer')
```


Maps 
=======================================================================

### Recent Downlads

Summary  
=======================================================================


About  
=======================================================================

